---
title: "p8160_hw4_jsg2145"
author: "Jared Garfinkel"
date: "4/19/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(MASS)
library(parallel)
library(boot)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
blue <- c(4,69,87,35,39,79,31,79,65,95,68,
          62,70,80,84,79,66,75,59,77,36,86,
          39,85,74,72,69,85,85,72)

red <- c(62,80,82,83,0,81,28,69,48,90,63,
        77,0,55,83,85,54,72,58,68,88,83,78,
        30,58,45,78,64,87,65)

acui <- data.frame(str = c(rep(0,20),
                       rep(1,10)),
                 red,
                 blue)
```

## Part 1i

```{r}
one_sui_red = acui %>% 
  filter(str == 1) %>% 
  dplyr::select(red)

one_sui_blue = acui %>% 
  filter(str == 1) %>% 
  dplyr::select(blue) %>% 
  as.tibble()
```

```{r}
teststat <- function(x = pull(one_sui_red, red), y = pull(one_sui_blue, blue)) {
  return((mean(y) - mean(x))/(var(x)/length(x) + var(y)/length(y)))
}

boottest <- function(x = pull(one_sui_red, red), y = pull(one_sui_blue, blue), nboot = 200) {
  combmean <- mean(c(x, y))
  # The mean of the combined sample
  teststatvec <- rep(NA, nboot)
  adjx <- x - mean(x) + combmean
  # The adjusted X’s will have mean=combmean
  adjy <- y - mean(y) + combmean
  # The adjusted X’s will have mean=combmean
  for(b in 1:nboot) {
    teststatvec[b] <- teststat(sample(adjx, replace=T),
                               sample(adjy, replace=T))
  }
  return(list(bootpval = sum(teststat(x, y) < teststatvec)/nboot, 
              teststatvec = teststatvec))
}
```



```{r, warning = TRUE}
teststat()

boottest()
```

```{r}
paired_sample_df = acui %>% 
  filter(str == 0) %>% 
  mutate(diff = red - blue) %>%
  as.tibble()
```

```{r}
set.seed(22)
teststat_paired <- function(x = pull(paired_sample_df, diff)) {
    return(mean(x)/(sqrt(var(x)/length(x))))
}

set.seed(22)
boottest_paired <- function(diff = pull(paired_sample_df, diff), nboot=200) {
  teststatvec <- rep(NA, nboot)
  adjdiff <- diff - mean(diff)
  for (b in 1:nboot) {
    teststatvec[b] <- teststat_paired(sample(adjdiff, replace = TRUE))
  }
  return(list(bootpval = sum(teststat_paired(diff) < teststatvec)/nboot, 
              teststatvec = teststatvec))
}

set.seed(22)
boottest_paired()
```

## Problem 1b

```{r}
np = function (size = 200, func) {
  boottest_boot = func()$teststatvec %>% 
    sample(size = 200, replace = TRUE)
  n = sum(boottest_boot > func()$bootpval)
  np = n/size
  return(np)
}

treffect_lower_paired = qnorm(.025, mean = mean(sample(paired_sample_df$diff, size = length(paired_sample_df$diff), replace = TRUE)))
treffect_upper_paired = qnorm(.025, mean = mean(sample(paired_sample_df$diff, size = length(paired_sample_df$diff), replace = TRUE)))

c(treffect_lower_paired, treffect_upper_paired)
```


The p-value for the paired samples is `r np(func = boottest_paired)` and the p-value for the two-sample data is `r np(func = boottest)`, which shows a difference for different types of patients.

The confidence interval for the effect size in paired data is (`r treffect_lower_paired %>% round(3)`, `r treffect_upper_paired %>% round(3)`), which is not what would be expected based on the p-values.

## in parallel

```{r}
set.seed(22)
nCores <- detectCores() # detect numbers of available cores 
cl = makeCluster(nCores)
cl
system.time({
res2 = boottest_paired()
})
stopCluster(cl)
```

## Problem 2

```{r}
data(galaxies)
galaxies %>%
  as_tibble() %>% 
  ggplot(aes(x = value)) +
  geom_histogram()
plot(density(galaxies/1000, bw=1.5))
plot(density(galaxies/1000, bw=3.5))
```

```{r}
#calculate the number of modes in the density
den <- density(galaxies/1000, bw=1.5)
den.s <- smooth.spline(den$x, den$y, all.knots = TRUE, spar = 0.8)
s.1 <- predict(den.s, den.s$x, deriv=1)
nmodes <- length(rle(den.sign <- sign(s.1$y))$values)/2
```

```{r}
unif_dens = function(u){
  u = runif(82)
}

data = galaxies

x = rep(NA, 82)
for (i in 1:82) {
  x[i] = unif_dens(u)[[i]] %*% data[[i]]
}

h = (4 * min(sd(data), IQR(data))/(3*200))^(1/5)

kernel = function(x) {
  mean(unif_dens((x - data)/h))/h
}

kernel(x)

kpdf = function(x) {
  sapply(x, kernel)
}

kpdf(x)

plot(x,unif_dens(x), type="l", col="red") 
par(new=T)
plot(x,kpdf(x),type="l",ylim=c(0,0.23),xlab="",ylab="",axes=F)
```

